Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-12-02 paper/ucl_tbr_paper.tex
minor content and typesetting adjustments
increase size of captions in fig. 6 plots

\usepackage{siunitx}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
\usepackage{isotope}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tabularx}

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\newcommand{\DDO}{D\textsubscript{2}O}

@@

@@

% TODO: revise these
\keywords{machine learning, surrogate model, regression, Monte Carlo simulation, tritium breeding, adaptive sampling}
\submitto{\NF}
\maketitle
\ioptwocol

@@

\section{Methodology}
\label{sec:methodoglogy}
\input{methodology}

>>>>

\usepackage{siunitx}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
\usepackage{isotope}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tabularx}

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\newcommand{\DDO}{D\textsubscript{2}O}
\definecolor{datacolor}{RGB}{72,36,117}

@@

\newcommand{\surrogateplot}[6]{
\begin{tikzpicture}
	\node[anchor=south west,inner sep=0] at (0,0){\includegraphics[width=\textwidth]{#1}};
	\draw[black,fill=white,line
		width=0.05mm,align=right,font=\fontsize{5.5}{6.5}\selectfont]
		(0.42,#6) rectangle
		(2.45,2.5) node[pos=.5] {
			\\[0.1ex]
			$\mathrm{MAE} = \num{#2}$\\
			$S = \num{#3}$\\
			$R^2 = \num{#4}$\\
			$R^2_{\text{adj.}} = \num{#5}$
		};
	\draw[black,fill=white,line
		width=0.05mm,align=left,font=\fontsize{5.5}{7.5}\selectfont]
		(2.02,1.43) rectangle
		(4.05,0.38) node[pos=.5] {
			{\color{red}
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Ideal model\\
			{\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Trained model\\
			\hskip3pt\raisebox{0.25ex}{\scalebox{0.75}{\color{datacolor}\textbullet}}\hskip4pt Data
		};
\end{tikzpicture}}

@@

\keywords{machine learning, surrogate model, regression, fast approximation,
Monte Carlo simulation, OpenMC, Paramak, tritium breeding, adaptive sampling}
\submitto{\NF}
\maketitle
\ioptwocol

@@

\section{Methodology}
\label{sec:methodology}
\input{methodology}
